Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-08-26 paper/paper.Rmd
comments from @bisaloo

  The ECDC forecast hub requests forecasts for 1 to 4 week forecast horizon and requires forecasts to use a pre-specified format with 23 quantiles of the predictive probability distribution.
  No restrictions were placed on who could submit forecasts and the hub team actively invited particupation from research groups known to be involved with COVID-19 forecasting projects.
  Forecasters used a wide range of forecasting methods including statistical approaches, mechanistic models including deterministic ordinary differential equation models and agent based model, semi-mechanistic models, expert elicitation models, and ensembles of mutliple approaches (described at https://covid19forecasthub.eu/community.html).
  Teams submitted forecasts at the latest two days after the complete dataset for the latest forecasting week became available and were allowed to use all data available at the time of submission. 
  The ensemble forecast was constructed by taking the median of all predictive quantiles without the exlusion of any valid submitted forecast (where validity was defined as passing minimal formatting checks by the hub team). 
  Submitted forecasts and target observations are freely available with a permissive open-source license from the ECDC forecast hub GitHub repository. We provide code in the repository of this study to streamline access.

@@

In order to standardise forecasts across forecast locations we first normalised both weekly notified test positive cases and forecast test positive cases by the population in the forecast region scaled to be a rate per 10,000 people.
We then evaluated a subset of forecasts from the following countries Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom visually by forecast horizon (1-4 weeks) for both the ensemble and surrogate model.

@@

We extracted forecasts starting from the 15th of January until the 19th of July 2022 for all countries covered by the ECDC forecasting hub (all ECDC nations and the UK making `r locations` unique locations). In total `r nrow(metadata)` forecasts were made across all locations, `r forecast_dates` forecast dates from `r models` independent forecast models (including the ECDC baseline model). Of these models, `r length(global_models)` forecasted in at least 30 locations including our original submission  (referred to as `epiforecasts-EpiNow2` by the hub), and our surrogate model. Of the remaining models submitted `r length(local_models)` were submitted in only one location. These models were gernerally submitted to a subset of locations with particular clustering in Germany and Poland (likely due to the folding of the German/Poland forecasting hub into the ECDC forecasting hub project). Italy was also an outlier with `r single_locs_models_per_loc[location == "IT", n]` models that submitted nowhere else. `r nrow(partial_models)` models submitted for between 3 and 30 locations and all these models varied the number of locations they submitted forecasts for over time, potentially indicating manual curation or models targeted at specific conditions.

>>>>

  The ECDC forecast hub requests forecasts for 1 to 4 week forecast horizon and requires forecasts to use a pre-specified format with 23 quantiles of the predictive probability distribution.
  No restrictions were placed on who could submit forecasts and the hub team actively invited particupation from research groups known to be involved with COVID-19 forecasting projects.
  Forecasters used a wide range of forecasting methods including statistical approaches, mechanistic models including deterministic ordinary differential equation models and agent based model, semi-mechanistic models, expert elicitation models, and ensembles of mutliple approaches (described at https://covid19forecasthub.eu/community.html).
  Teams submitted forecasts at the latest two days after the complete dataset for the latest forecasting week became available and were allowed to use all data available at the time of submission. 
  The ensemble forecast was constructed by taking the median of all predictive quantiles without the exlusion of any valid submitted forecast (where validity was defined as passing minimal formatting checks by the hub team). 
  Submitted forecasts and target observations are freely available from the ECDC forecast hub GitHub repository. We provide code in the repository of this study to streamline access.

@@

In order to standardise forecasts across forecast locations we first normalised both weekly notified test positive cases and forecast test positive cases by the population in the forecast region scaled to be a rate per 10,000 people.
We then evaluated a subset of forecasts from the following countries Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom visually by forecast horizon (1-4 weeks) for both the ensemble and surrogate model. 
These countries were selected in order to include forecasts based on different numbers and types of submitted forecast models, to be at least somewhat representative of the full sample of forecast locations, and to include nations for which the authors had a good understanding of local data and transmission dynamics in the study period.

@@

We extracted forecasts starting from the 15th of January until the 19th of July 2022 for all countries covered by the ECDC forecasting hub (all ECDC nations and the UK making `r locations` unique locations).
In total `r nrow(metadata)` forecasts were made across all locations, `r forecast_dates` forecast dates from `r models` independent forecast models (including the ECDC baseline model).
Of these models, `r length(global_models)` forecasted in at least 30 locations including our original submission  (referred to as `epiforecasts-EpiNow2` by the hub), and our surrogate model.
Of the remaining models submitted `r length(local_models)` were submitted in only one location.
These models were generally submitted to a subset of locations with particular clustering in Germany and Poland (likely due to the folding of the German/Poland forecasting hub into the ECDC forecasting hub project).
Italy was also an outlier with `r single_locs_models_per_loc[location == "IT", n]` models that submitted nowhere else.
`r nrow(partial_models)` models submitted for between 3 and 30 locations and all these models varied the number of locations they submitted forecasts for over time, potentially indicating manual curation or models targeted at specific conditions.
